### 2020-09-14 LaTeX/sections/paper.tex

>>>>

\subsection*{Static Analysis of \cm}
We used \textit{Slither}~\footnote{https://github.com/crytic/slither} and \textit{SmartCheck}~\footnote{https://tool.smartdec.net} security audit tools on the \cm to check the code  for vulnerabilities and bad practices. We received 100\% success rate in a total of 67 audits performed by considering 'Informational' checks as 'Passed'.
